---
title: "Attendance Rate VS Teachers Masters Degree"
author: "Ranjitha Elaprolu"
date: "11/07/2017"
output: html_document
---


###Research Question: Does the percentage of teachers with masters degree has an impact on Students Dropout Rate

### R Plots for Graphical Representation on the research Question




```{r}
library(readxl)	

library(ggrepel)

library(ggplot2)
```

Create a dataframe for the dataset, cleaned the dataset.
```{r}
setwd("C:/users/Ramya/Documents")
set2 <- readxl::read_xlsx("Set 2.xlsx")
set2 <- set2[set2$`Attendance Rate` > -1,]
```

## Basic Plot on Dropout rate VS Attendance Rate

```{r}
plot(set2$`Attendance Rate`,set2$`Dropout Rate`, main = "Attendance Rate VS Dropout Rate",xlab = "Attendance Rate",ylab = "Dropout Rate",col.lab="blue",cex.lab=0.75,cex=2,col="red")
```

### ggplot for Attendance rate VS Dropout rate.  

Plotted the ggplot with point and smooth function which gives a layerof smooth surface covering the scattered points based on the values.   This is a clear and easy understanding to interpret how the dropout rate has been dropped for increasing attendance rate.  
```{r}
p1 <- ggplot(set2, aes(x = `Attendance Rate`, y = `Dropout Rate`))
p1 + geom_point(aes(color = set2$`Attendance Rate`)) +  geom_smooth()
```

### ggplot: Attendance rate VS Dropout rate for year 2015-2016.
The label on the graph represents the district and state data. From the table the values of district schools are high compared to the state schools.
```{r}
yr20152016 <- set2[set2$`School Year`== 20152016, ]
p1 <-  ggplot(yr20152016, aes(x = `Attendance Rate`, y = `Dropout Rate`, main ="Year 2015-2016"))
p1 + geom_point(aes(color = `Attendance Rate`)) +  geom_smooth() + geom_text(aes(label=Type),size=3)
```

### ggplot: Log Attendance rate VS Dropout rate for year 2015-2016.  
Applied arthimetic function log on the attendance rate column to display and scattered value which gives a clear picture on the decreaing dropout rate for increasing attendance rate.  
That is being displayed in the below Graph.
```{r}
p1 <-  ggplot(yr20152016, aes(x = log(`Attendance Rate`), y = `Dropout Rate`))
p1 + geom_point(aes(color = `Attendance Rate`)) +  geom_smooth()
```
