---
title: "Dropout Rate VS Teachers Masters Degree"
author: "Ranjitha Elaprolu"
date: "11/07/2017"
output: html_document
---


###Research Question: Does the percentage of teachers with masters degree has an impact on Students Dropout Rate

### R Plots for Graphical Representation on the research Question




```{r}
library(readxl)	

library(ggrepel)

library(ggplot2)
```

Create a dataframe for the dataset, cleaned the dataset.
```{r}
setwd("C:/users/Ramya/Documents")
set3 <- readxl::read_xlsx("Set 3.xlsx")
set3 <- set3[set3$`Dropout Rate` > -1,]
```

#### Basic plot on Teachers with master's degree VS Dropout Rate.
```{r}
plot(set3$`Teachers with Masters Degree`,set3$`Dropout Rate`,main = "Percentage of Teachers with masters degree VS Dropout Rate",xlab = "% of teachers with master's Degree",ylab = "Dropout Rate",col.lab="blue",cex.lab=0.75,cex=2,col="red")
```

### Group: School Year on Teachers with masters degree VS Dropout Rate.

#### ggplot on Teachers with master's degree VS Dropout Rate. 
* Using ggplot created the plot for the same parameters.
* And then used the facet function to split the plot based on the school year. 
* By this we will know which year we had many dropout rates.
```{r}
plt1 <- ggplot(set3, aes(x = `Teachers with Masters Degree`, y = `Dropout Rate`))
(plt2 <- plt1 + geom_line() + facet_wrap(~`School Year`))
```

### Group County wise Teachers with masters degree VS Dropout Rate.
#### ggplot for teachers with masters degree VS Dropout Rate.
Created the plot using ggplot package.  I had interpreted the data for each county on the same parameters.   
By this we can figure out which school had the varying dropout rate with respect to percentage of teachers with masters degree.
```{r}
plt1 <- ggplot(set3, aes(x = `Teachers with Masters Degree`, y = `Dropout Rate`))
(plt2 <- plt1 + geom_line() + facet_wrap(~`County`))
```



